%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Short Sectioned Assignment
% LaTeX Template
% Version 1.0 (5/5/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[paper=a4, fontsize=10pt]{scrartcl} % A4 paper and 11pt font size
\usepackage{geometry}
\geometry{margin=2cm}
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
%\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage[utf8]{inputenc} 
\usepackage{amsmath,amsfonts,amsthm} % Math packages

\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage{graphicx}

\usepackage{sectsty} % Allows customizing section commands
%\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps
\geometry{left=1cm}
\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height

\title{	
\normalfont \normalsize 
\textsc{University of Freiburg} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Exercise 2: Policy \& Value Iteration \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Nico Ott 4214197\\ Lior Fuks 4251285 \\Hendrik Vloet 4324249}

\date{\normalsize\today} % Today's date or a custom date

\begin{document}

\maketitle % Print the title

%----------------------------------------------------------------------------------------
%	PROBLEM 1
%----------------------------------------------------------------------------------------
\section{Policy Iteration}
- See according code file \textbf{policy\_iteration.py}


\section{Value Iteration}
\subsection*{a)}
- See according code file \textbf{value\_iteration.py}
\subsection*{b)}
\begin{itemize}

\item The policy iteration algorithm consists of two explicit components, the policy evaluation and the policy improvement step. These two steps are looped until convergence is achieved:\\
$ \pi_0 \xrightarrow{\text{eval}} v_{\pi_0} \xrightarrow{\text{improve}} \pi_1 \xrightarrow{\text{eval}} ... \xrightarrow{\text{improve}} \pi_* \xrightarrow{\text{eval}} v_* $ \\
Value iteration does not use an explicit policy evaluation step: $v_1 \rightarrow v_2 \rightarrow ...  \rightarrow v_*$.\\
 After convergence to $v_*$ the optimal policy $\pi_*$ is instantly known.
In praxis, convergence is obtained by check the difference of the two latest value functions. If it does only change for a small amount ($\sim$ 0.0001). 
\item One drawback of policy iteration is, that it can be computationally inefficient because we have to wait until it converges and the algorithm only does that in its limits (obviously). Value iteration converges much faster due to the lack of an explicit policy evaluation.

\item value iteration uses the Bellman optimality equation in order to update their value function and policy iteration uses the bellman expectation equation and then greedily improves its policy. 
\item Similarity: value iteration is equivalent to policy iteration if policy iteration is terminated after one complete sweep of all states.\\
\end{itemize}
\clearpage
\section{Experiences}
\begin{itemize}
	\item \textbf{Nico}
	\begin{itemize}
		\item Invested Time:
		\begin{itemize}
			\item Meeting: 0h; Was on my sisters wedding on Friday. Missed the meeting :-(
			\item Lecture: 3h; Just watched the lecture and took notes (but way too late)
			\item Exercise: 2h; I was sick from last tuesday on and had no energy for the assignment.\\
		Plus, there was my sisters wedding on Friday (and Saturday), where I had to organize some stuff as best man.
		\end{itemize}		
		\item General:
		\begin{itemize}
			\item It was really unfortunate for me, that nobody wrote a single thing in the Google Doc about last meeting.
			\item I get the feeling that I'm one of the few that are actually using this opportunity.
			\item Maybe the other students tend to use the Ilias forum if they have questions
			\item But at least for flipped classroom some kind of protocol should always be available
		\end{itemize}
	\end{itemize}

	\item \textbf{Hendrik}
	\begin{itemize}
		\item Invested time:
		\begin{itemize}
			\item Meeting: 2h
			\item Lecture 3: 3h
			\item Exercise : $\sim$ 24h
		\end{itemize}
		\item General:
		\begin{itemize}
			\item understanding issues with the unit test structure of the python environment
			\item I had trouble comprehending why we had to go for a deterministic policy, thanks to rr114\_uni-freiburg  for helping out!
			\item Sadly, protocol morale for the google doc seems rather low. I added some things regarding the video lecture and the according discussion last time.		
		\end{itemize}
	\end{itemize}
\end{itemize}
	

\end{document}